TBD

### 2021-03-12 outputs/paper/paper.Rmd
update

ggplot(EDA, aes(x = post_favor_Warren,fill=treat)) +
  geom_histogram(bins=15,color="white") +
  facet_grid(treat ~ .)+
  scale_fill_manual(values = c("#DB7558", "#FFCF57","#8FCDD4","#F6A6B6", "#ACD8CB","#3E737D"))+
  xlab("Feelings towards Sanders")+
  ggtitle("Distribution of feelings towards Sanders in six different conditions")+
  theme_minimal()

>>>>

ggplot(EDA, aes(x = post_favor_Warren,fill=treat)) +
  geom_histogram(bins=15,color="white") +
  facet_grid(treat ~ .)+
  scale_fill_manual(values = c("#DB7558", "#FFCF57","#8FCDD4","#F6A6B6", "#ACD8CB","#3E737D"))+
  xlab("Feelings towards Sanders")+
  ggtitle("Distribution of feelings towards Warren in six different conditions")+
  theme_minimal()
